Data-based completion of initial grey-box models for process control

### 2020-09-11 twccc.tex
talk structure.

\title[Data completion of initial gray box models for process control and optimization]{Data completion of initial gray box models for process control and optimization}
\date{September 15, 2020}
\author[Kumar and Rawlings]{\large Pratyush Kumar and James B. Rawlings}
\institute[UCSB]{
	\begin{minipage}{4in}
		\vspace{-10pt}
		\centering
		\raisebox{-0.1\height}{\includegraphics[width=0.25\textwidth]{UCSB_seal}}
		%\hspace*{.2in}
		%\raisebox{-0.5\height}{\includegraphics[width=0.25\textwidth]{jci_logo}}
	\end{minipage}
	\vspace{10pt}
	\newline
	{\large Department of Chemical Engineering}
	\vspace{10pt}
	\newline
	{\large TWCCC Meeting (Virtual)}}
	%\vspace{10pt}
	%\newline
	%{\large Austin, TX}}

@@

% MPC intro frame
\begin{frame}{Idea.}
Hi.
\end{frame}

>>>>

\title[Data-based completion of initial grey-box models for process control]{Data-based completion of initial grey-box models for process control}
\date{September 15, 2020}
\author[Kumar and Rawlings]{\large Pratyush Kumar and James B. Rawlings}
\institute[UCSB]{
	\begin{minipage}{4in}
		\vspace{-10pt}
		\centering
		\raisebox{-0.1\height}{\includegraphics[width=0.25\textwidth]{UCSB_seal}}
		%\hspace*{.2in}
		%\raisebox{-0.5\height}{\includegraphics[width=0.25\textwidth]{jci_logo}}
	\end{minipage}
	\vspace{10pt}
	\newline
	{\large Department of Chemical Engineering}
	\vspace{10pt}
	\newline
	{\large TWCCC Meeting (Virtual)}}
	%\vspace{10pt}
	%\newline
	%{\large Austin, TX}}

@@

% MPC intro frame
\begin{frame}{Grey-box models and undermodeling}
Hi.
\end{frame}

\begin{frame}{Completing grey-box models from operational data}
	Hi.
\end{frame}

\begin{frame}{Simulation example}
	Hi.
\end{frame}

\begin{frame}{Simulation example -- validation data}
	Hi.
\end{frame}
